Errata

### 2025-04-06 tex/Manuscript-1.tex
Refactor methodology and results sections: update chapter and section numbering, adjust labels and references, and improve table and figure captions for clarity and consistency.
Update manuscript title and author list in Manuscript-3.tex; change bibliography style to natbib
Refactor code structure for improved readability and maintainability

\begin{small}
    \begin{justify}
    \textsuperscript{1} University of Tübingen, Department of Geosciences, Soil Science and Geomorphology, Rümelinstr. 19-23, 72070 Tübingen, Germany

    \textsuperscript{2} Technical University of Munich, Soil Science, Emil-Ramann-Str. 2, 85354 Freising, Germany

    \textsuperscript{3} GFZ German Research Centre for Geosciences, Section 5.3 Geomicrobiology, Telegrafenberg, 14473 Potsdam, Germany

    \textsuperscript{4} Department of Geosciences and Natural Resource Management, University of Copenhagen, Copenhagen, Denmark

    \textsuperscript{5} Universidad de Atacama, Centro Regional de Investigación y Desarrollo Sustentable de Atacama (CRIDESAT), Copayapu 485, Copiapó, Chile

    \textsuperscript{6} Universidad de Chile, Facultad de Ciencias Agronómicas, Av. Santa Rosa \#11315, La Pintana, 8820808 Santiago, Chile

    \textsuperscript{7} University of Potsdam, Institute of Geosciences, Karl-Liebknecht-Str. 24-25, 14476 Potsdam, Germany
    \end{justify}
\end{small}

@@

>>>>

\begin{scriptsize}
    \begin{justify}
        \textsuperscript{1} University of T{\"u}bingen, Department of Geosciences, Soil Science and Geomorphology, R{\"u}melinstr. 19--23, 72070 T{\"u}bingen, Germany\\
        \textsuperscript{2} Technical University of Munich, Soil Science, Emil-Ramann-Str. 2, 85354 Freising, Germany\\
        \textsuperscript{3} GFZ German Research Centre for Geosciences, Section 5.3 Geomicrobiology, Telegrafenberg, 14473 Potsdam, Germany\\
        \textsuperscript{4} Department of Geosciences and Natural Resource Management, University of Copenhagen, Copenhagen, Denmark\\
        \textsuperscript{5} Universidad de Atacama, Centro Regional de Investigaci{\'o}n y Desarrollo Sustentable de Atacama (CRIDESAT), Copayapu 485, Copiap{\'o}, Chile\\
        \textsuperscript{6} Universidad de Chile, Facultad de Ciencias Agron{\'o}micas, Av. Santa Rosa \#11315, La Pintana, 8820808 Santiago, Chile\\
        \textsuperscript{7} University of Potsdam, Institute of Geosciences, Karl-Liebknecht-Str. 24--25, 14476 Potsdam, Germany
    \end{justify}
\end{scriptsize}

@@

\bibliographystyle{natbib}
\bibliography{literatur}

### 2025-04-06 tex/Manuscript-2.tex
Update manuscript title and author list in Manuscript-3.tex; change bibliography style to natbib
Refactor code structure for improved readability and maintainability

>>>>

\begin{center}
  \textbf{\Large Manuscript 2}

  \vspace{0.3cm}
  \textit{Geoderma}\\
  \textit{Submitted}

  \vspace{0.5cm}

  Nicolás Riveras-Muñoz\textsuperscript{1*}, Steffen Seitz\textsuperscript{1}, Corinna Gall\textsuperscript{1}, Victoria Rodríguez\textsuperscript{2}, Kristina Witzgall\textsuperscript{3}, Peter Kühn\textsuperscript{1}, Carsten W. Mueller\textsuperscript{4,5}, Rómulo Oses\textsuperscript{6}, Oscar Seguel\textsuperscript{7}, Dirk Wagner\textsuperscript{2,8}, and Thomas Scholten\textsuperscript{1}

  \vspace{0.2cm}
\end{center}

\begin{scriptsize}
  \begin{justify}
    \textsuperscript{1}University of T{\"u}bingen, Department of Geosciences, Soil Science and Geomorphology, R{\"u}melinstr. 19--23, 72070 T{\"u}bingen, Germany\\
    \textsuperscript{2}GFZ Helmholtz Centre for Geosciences, Section Geomicrobiology, Telegrafenberg, 14473 Potsdam, Germany\\
    \textsuperscript{3}Technical University of Munich, Soil Science, Emil-Ramann-Str. 2, 85354 Freising, Germany\\
    \textsuperscript{4}Technische Universit{\"a}t Berlin, Ernst-Reuter-Platz 1, 10587 Berlin, Germany\\
    \textsuperscript{5}Department of Geosciences and Natural Resource Management, University of Copenhagen, Copenhagen, Denmark\\
    \textsuperscript{6}Universidad de Atacama, Centro Regional de Investigaci{\'o}n y Desarrollo Sustentable de Atacama (CRIDESAT), Copayapu 485, Copiap{\'o}, Chile\\
    \textsuperscript{7}Universidad de Chile, Facultad de Ciencias Agron{\'o}micas, Av. Santa Rosa \#11315, La Pintana, 8820808 Santiago, Chile \\
    \textsuperscript{8}University of Potsdam, Institute of Geosciences, Karl-Liebknecht-Str. 24--25, 14476 Potsdam, Germany
  \end{justify}
\end{scriptsize}

\vspace{0.5cm}
\begin{center}
  Submitted: March 17, 2025\\
\end{center}
\cleardoublepage

### 2025-04-06 tex/Manuscript-3.tex
Refactor code structure for improved readability and maintainability

  \begin{small}
    \begin{justify}

        \textsuperscript{1}GFZ German Research Centre for Geosciences, Section Geomicrobiology, Potsdam, Germany,

        \textsuperscript{2}Soil Science, TUM School of Life Sciences, Technical University of Munich, Freising-Weihenstephan, Germany,

        \textsuperscript{3}Department of Geosciences, Soil Science and Geomorphology, University of Tübingen, Tübingen, Germany

        \textsuperscript{4}Centro Regional de Investigación y Desarrollo Sustentable de Atacama (CRIDESAT), Universidad de Atacama, Copiapó, Chile

        \textsuperscript{5}Institute of Biochemistry and Biology, University of Potsdam, Potsdam, Germany

        \textsuperscript{6}GFZ German Research Centre for Geosciences, Section Geomorphology, Potsdam, Germany

        \textsuperscript{7}Institute for Ecology, Chair of Soil Science, Technische Universitaet Berlin, Berlin, Germany

        \textsuperscript{8}Department of Geosciences and Natural Resource Management, University of Copenhagen, Copenhagen, Denmark

        \textsuperscript{9}Facultad de Ciencias Agronómicas, Universidad de Chile, Santiago, Chile

        \textsuperscript{10}Institute of Geosciences, University of Potsdam, Potsdam, Germany

    \end{justify}
  \end{small}

>>>>

  \begin{scriptsize}
    \begin{justify}

      \textsuperscript{1}GFZ German Research Centre for Geosciences, Section Geomicrobiology, Potsdam, Germany\\
      \textsuperscript{2}Soil Science, TUM School of Life Sciences, Technical University of Munich, Freising-Weihenstephan, Germany\\
      \textsuperscript{3}Department of Geosciences, Soil Science and Geomorphology, University of T{\"u}bingen, T{\"u}bingen, Germany\\
      \textsuperscript{4}Centro Regional de Investigaci{\'o}n y Desarrollo Sustentable de Atacama (CRIDESAT), Universidad de Atacama, Copiap{\'o}, Chile\\
      \textsuperscript{5}Institute of Biochemistry and Biology, University of Potsdam, Potsdam, Germany\\
      \textsuperscript{6}GFZ German Research Centre for Geosciences, Section Geomorphology, Potsdam, Germany\\
      \textsuperscript{7}Institute for Ecology, Chair of Soil Science, Technische Universit{\"a}t Berlin, Berlin, Germany\\
      \textsuperscript{8}Department of Geosciences and Natural Resource Management, University of Copenhagen, Copenhagen, Denmark\\
      \textsuperscript{9}Facultad de Ciencias Agron{\'o}micas, Universidad de Chile, Santiago, Chile\\
      \textsuperscript{10}Institute of Geosciences, University of Potsdam, Potsdam, Germany

    \end{justify}
  \end{scriptsize}

### 2025-04-06 tex/Manuscript-4.tex
Refactor code structure for improved readability and maintainability

  \begin{small}
    \begin{justify}

        \textsuperscript{1}GFZ German Research Centre for Geosciences, Section Geomicrobiology, Telegrafenberg D-14473 Potsdam, Germany

        \textsuperscript{2}Centro Regional de Investigacion y Desarrollo Sustentable de Atacama, Universidad de Atacama (CRIDESAT UDA), Copayapu 484, Copiapó, Chile

        \textsuperscript{3}University of Tübingen, Soil Science and Geomorphology, Rümelinstrasse 19-23, D-72070 Tübingen, Germany

        \textsuperscript{4}Institute of Ecology, Chair of Soil Science, Technische Universität Berlin, 10587 Berlin, Germany

        \textsuperscript{5}Department of Geosciences and Natural Resource Management, University of Copenhagen, 1350 Copenhagen K, Denmark

        \textsuperscript{6}Universidad de Chile, Facultad de Ciencias Agronómicas, Av. Santa Rosa \#11315, La Pintana, 8820808 Santiago, 15 Chile

        \textsuperscript{7}University of Potsdam, Institute of Geosciences, Karl-Liebknecht-Strasse 24-25, D-14476 Potsdam, Germany

    \end{justify}
  \end{small}

>>>>

  \begin{scriptsize}
    \begin{justify}

      \textsuperscript{1}GFZ German Research Centre for Geosciences, Section Geomicrobiology, Telegrafenberg D-14473 Potsdam, Germany\\
      \textsuperscript{2}Centro Regional de Investigaci{\'o}n y Desarrollo Sustentable de Atacama, Universidad de Atacama (CRIDESAT UDA), Copayapu 484, Copiap{\'o}, Chile\\
      \textsuperscript{3}University of T{\"u}bingen, Soil Science and Geomorphology, R{\"u}melinstrasse 19--23, D-72070 T{\"u}bingen, Germany\\
      \textsuperscript{4}Institute of Ecology, Chair of Soil Science, Technische Universit{\"a}t Berlin, 10587 Berlin, Germany\\
      \textsuperscript{5}Department of Geosciences and Natural Resource Management, University of Copenhagen, 1350 Copenhagen K, Denmark\\
      \textsuperscript{6}Universidad de Chile, Facultad de Ciencias Agron{\'o}micas, Av. Santa Rosa \#11315, La Pintana, 8820808 Santiago, Chile\\
      \textsuperscript{7}University of Potsdam, Institute of Geosciences, Karl-Liebknecht-Strasse 24--25, D-14476 Potsdam, Germany

    \end{justify}
  \end{scriptsize}
